p-adic stability in linear algebra

### 2015-04-26 examples/stability.tex
Added 2 remarks + 1 item in the biblio

In \cite{caruso-roe-vaccon:14a}, we suggest the 
use of lattices to represent the precision of elements in 
$K$-vector spaces.  We shall contrast this approach with the
\emph{coordinate-wise method} used in Sage and Magma,
where the precision of an element is specified by giving the precision
of each coordinate separately.

@@

This proposition enables the \emph{lattice method} of tracking precision,
where the precision of the input is specified as a lattice $H$ and precision
is tracked via differentials of the steps within a given algorithm.
The equality sign in Eq.~\eqref{eq:firstorder} shows that this method
yields the optimum possible precision.

@@

\caption{Loss of precision for LU factorization}
\label{fig:LU}
\end{figure}
%

@@

@@

\caption{Average loss of precision in Algorithm 2}
\label{fig:vectorspace}
\end{figure}
%
Figure \ref{fig:vectorspace} shows the losses of precision when
executing Algorithm 2 with various inputs $n$ (the input $N$ is
always chosen sufficiently large so that it does not affect the
behavior of precision). The \emph{Coord-wise} column corresponds to
the standard way of tracking precision. On the other hand, in the two 
last columns, the precision is tracked using lattices. The \emph{Diffused}
column gives the amount of diffused precision, factored to be comparible
to the Coord-wise column. 
The fact that only negative numbers appear in this column means that we 
are actually always gaining precision with this model! Finally, the 
\emph{Projected} column gives the precision loss after projecting the lattice
precision onto coordinates.

>>>>

In \cite{caruso-roe-vaccon:14a}, we suggest the 
use of lattices to represent the precision of elements in 
$K$-vector spaces.  We shall contrast this approach with the
\emph{coordinate-wise method} used in Sage, % and Magma,
where the precision of an element is specified by giving the precision
of each coordinate separately and is updated after each basic
operation.

@@

This proposition enables the \emph{lattice method} of tracking precision,
where the precision of the input is specified as a lattice $H$ and precision
is tracked via differentials of the steps within a given algorithm.
The equality sign in Eq.~\eqref{eq:firstorder} shows that this method
yields the optimum possible precision. 
We refer to \cite[\S 4.1]{caruso-roe-vaccon:14a} for a more complete 
exposition.

@@

\vspace{-0.4cm}

\caption{Loss of precision for LU factorization}
\label{fig:LU}

\end{figure}
%

@@

%\vspace{-1ex}\noindent\hrulefill

%\medskip

@@

\vspace{-0.4cm}

\caption{Average loss of precision in Algorithm 2}
\label{fig:vectorspace}

\vspace{-0.2cm}

\end{figure}
%
Figure \ref{fig:vectorspace} shows the losses of precision when
executing Algorithm 2 with various inputs $n$ (the input $N$ is
always chosen sufficiently large so that it does not affect the
behavior of precision). The \emph{Coord-wise} column corresponds to
the standard way of tracking precision. On the other hand, in the two 
last columns, the precision is tracked using lattices. The \emph{Diffused}
column gives the amount of diffused precision, factored to be comparible
to the Coord-wise column. 
The fact that only negative numbers appear in this column means that we 
are actually always gaining precision with this model! Finally, the 
\emph{Projected} column gives the precision loss after projecting the lattice
precision onto coordinates.
